Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-19 paper/paper.tex
Update score table

(a) Number of workflows completed $N_c$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & TOTAL\tabularnewline
\hline
DPDS      &   57  & 45 &  18 &  14  &  0 & 134\tabularnewline
WA-DPDS   &    96 &  87  & 48  & 34  &  0 & 265\tabularnewline
SPSS     &    29  & 42  & 192  & 74  & 50 & 387\tabularnewline
\end{tabular}
\medskip

(b) Total amount of computing time completed $T_C$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & TOTAL\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & TOTAL\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip

M -- Montage; C -- CyberShake; L -- LIGO; E -- Epigenomics; S --SIPHT

\label{tab:num-dags-pareto}
\caption{Number of times each algorithm achieved the highest score for each
application (over all budgets and deadlines). Data based on total 525 runs on Pareto-distributed ensembles.}
\end{table}

>>>>

(a) Number of workflows completed $N_c$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   57  & 45 &  18 &  14  &  0 & 134\tabularnewline
WA-DPDS   &    96 &  87  & 48  & 34  &  0 & 265\tabularnewline
SPSS     &    29  & 42  & 192  & 74  & 50 & 387\tabularnewline
\end{tabular}
\medskip

(b) Total amount of computing time completed $T_C$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & All\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip

\label{tab:num-dags-pareto}
\caption{Number of times each algorithm achieved the highest score 
over all budgets and deadlines. Data from a total of 525 runs on 
Pareto-distributed ensembles for Montage (M), CyberShake (C), LIGO (L), 
Epigenomics (E), SIPHT (S).}
\end{table}
